What is a Scheme in Algebraic Geometry?

### 2020-11-25 blueprint.tex
Updates blueprint

\begin{definition}[entire ring]
	A ring $R$ is said to be entire if $1 \neq 0$ and there are no zero divisors in $R$. 
\end{definition}

@@

\begin{notation}
	If $\mathfrak{i}$ is an ideal of $R$, $V(\mathfrak{a})$ denotes the set of all prime ideals of $R$ which contain $\mathfrak{a}$. 
\end{notation}

@@

\begin{ex}
	Prove the equality $V(\sum \mathfrak{a}_i) = \bigcap V(\mathfrak{a}_i)$ for any familly of prime ideals.
\end{ex}

@@

\begin{cons}
	Let $U$ be an open subset of Spec $R$. We define $\mathscr{O}(U)$ to be the set of all functions 
	\[
	s: U \rightarrow \bigcup \limits_{\mathfrak{p} \in U} R_{\mathfrak{p}}
	\]
	such that $s(\mathfrak{p}) \in R_{\mathfrak{p}}$ for every $\mathfrak{p} \in U$ and such that for every $\mathfrak{p} \in U$, there exist a neighborhood $V$ of $\mathfrak{p}$, contained in $U$, and elements $r, f \in R$, such that for each $\mathfrak{q} \in V$, $f \notin \mathfrak{q}$ and $s(\mathfrak{q}) = r/f$. \\
	We endow $\mathscr{O}(U)$ with the sum and product of such functions and we take for the multiplicative unit the function that maps each $\mathfrak{p}$ on the multiplicative unit of $R_{\mathfrak{p}}$. \\
	Last, if $V \subseteq U$, then the morphism of rings $\mathscr{O}(U) \rightarrow \mathscr{O}(V)$ maps each $s \in \mathscr{O}(u)$ on its restriction $s \restriction V$. 
\end{cons}

\begin{ex}
	Prove $\mathscr{O}$ is a sheaf of rings on Spec $R$. 
\end{ex}

\begin{definition}[spectrum of a ring]
	The spectrum of the ring $R$ is the pair consisting of the topological space $Spec R$ together with the sheaf of rings $\mathscr{O}$.
\end{definition}

@@

\begin{definition}[morphism of ringed spaces]
	A morphism of ringed spaces from $(X, \mathscr{O}(X))$ to $(Y, \mathscr{O}(Y))$ is a pair $(f, f^{\sharp})$ consisting of a continuous map $f: X \rightarrow Y$ between topological spaces and a morphism $f^{\sharp}: \mathscr{O}_Y \rightarrow f_{*} \mathscr{O}_X$ of sheaves of rings.   
\end{definition}

@@

\begin{ex}
	Prove $(Spec R, \mathscr{O})$ is a locally ringed space.
\end{ex}

@@

\begin{definition}[affine scheme]
	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic to the spectrum $(Spec R, \mathscr{O})$ for some ring $R$. 
\end{definition}

>>>>

\begin{definition}[entire ring]
	A ring $R$ is said to be entire if it is commutative, $1 \neq 0$ and there are no zero divisors in $R$. 
\end{definition}

@@

\begin{notation}
	If $\mathfrak{a}$ is an ideal of $R$, $V(\mathfrak{a})$ denotes the set of all prime ideals of $R$ which contain $\mathfrak{a}$. 
\end{notation}

@@

\begin{ex}
	Prove the equality $V(\sum \mathfrak{a}_i) = \bigcap V(\mathfrak{a}_i)$ for any family of prime ideals.
\end{ex}

@@

\begin{cons}
	Let $U$ be an open subset of Spec $R$. We define $\mathscr{O}_R(U)$ to be the set of all functions 
	\[
	s: U \rightarrow \bigcup \limits_{\mathfrak{p} \in U} R_{\mathfrak{p}}
	\]
	such that $s(\mathfrak{p}) \in R_{\mathfrak{p}}$ for every $\mathfrak{p} \in U$ and such that for every $\mathfrak{p} \in U$, there exist a neighborhood $V$ of $\mathfrak{p}$, contained in $U$, and elements $r, f \in R$, such that for each $\mathfrak{q} \in V$, $f \notin \mathfrak{q}$ and $s(\mathfrak{q}) = r/f$. \\
	We endow $\mathscr{O}_R(U)$ with the sum and product of such functions and we take for the multiplicative unit the function that maps each $\mathfrak{p}$ on the multiplicative unit of $R_{\mathfrak{p}}$. \\
	Last, if $V \subseteq U$, then the morphism of rings $\mathscr{O}_R(U) \rightarrow \mathscr{O}_R(V)$ maps each $s \in \mathscr{O}_R(U)$ on its restriction to $V$. 
\end{cons}

\begin{ex}
	Prove $\mathscr{O}_R$ is a sheaf of rings on Spec $R$. 
\end{ex}

\begin{definition}[spectrum of a ring]
	The spectrum of the ring $R$ is the pair consisting of the topological space $Spec R$ together with the sheaf of rings $\mathscr{O}_R$.
\end{definition}

@@

\begin{definition}[morphism of ringed spaces]
	A morphism of ringed spaces from $(X, \mathscr{O}(X))$ to $(Y, \mathscr{O}(Y))$ is a pair $(f, \phi_f)$ consisting of a continuous map $f: X \rightarrow Y$ between topological spaces and a morphism $\phi_f: \mathscr{O}_Y \rightarrow f_{*} \mathscr{O}_X$ of sheaves of rings.   
\end{definition}

@@

\begin{ex}
	Prove $(Spec R, \mathscr{O}_R)$ is a locally ringed space.
\end{ex}

@@

\begin{definition}[affine scheme]
	An affine scheme is a locally ringed space $(X, \mathscr{O}_X)$ which is isomorphic to the spectrum $(Spec R, \mathscr{O}_R)$ for some ring $R$. 
\end{definition}
